CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-24 paper/ms.tex
Reorganize section 2

\section{Motivation}\label{sec:theory}

\subsection{Three-Field Approach}\label{ssec:three_field}
We describe the multi-field approach in full generality and state some
results.

First, we assume a measurement of each of $\xps{i}{j}$. The relevant variance
and covariances are \citep[e.g.][]{2015JCAP...03..034V}
\beq
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{.}
\end{split}
\eeq
We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
and $\xps{k}{i}$. We model each of these power spectra as
\beq
\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
\eeq
That is, we are only working in the regime where $r_{i,j}=1$. What this
translates to is that we may only perform this interloper removal on
sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
analogous to a similar procedure in galaxy surveys where only large-scale
information up to a $k_{\text{max}}$.

>>>>

\section{Multi-field Approach}\label{sec:theory}
We describe the multi-field approach in full generality and state some
results. First, we assume a measurement of each of $\xps{i}{j}$. The relevant
variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
\beq
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{.}
\end{split}
\eeq
We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
and $\xps{k}{i}$. We model each of these power spectra as
\beq
\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
\eeq
That is, we are only working in the regime where $r_{i,j}=1$. What this
translates to is that we may only perform this interloper removal on
sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
analogous to a similar procedure in galaxy surveys where only large-scale
information up to a $k_{\text{max}}$ where linear theory is applicable is used.
